Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-05 neurips-20/cvx-flats.tex
Updating T example

\begin{abstract}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

@@

Motivated by structural prediction and other problems with exponentially or infinitely large label sets, we are particularly interested in the \emph{prediction dimension} of a surrogate: the dimension $d$ of its prediction space $\reals^d$.
A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension can increase the computational and sample complexity of learning.
We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
%\raft{FYI Jessie: what used to be this last paragraph still didn't quite get where you want to be in terms of motivating the problem.  I'd suggest taking a careful look at the diff at some point to see what I changed and ask me if you don't see why.  Probably the biggest issue was in laying out the gap.  You often need to give more detail about what \emph{has} been done to say what hasn't.}

@@

Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
%\raft{Nice!  Love ``proxies'' here.}
In the case of a discrete target loss, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
%\raft{FYI Jessie: Two general points.  (1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.  Next time it would be more efficient if you made sure to balance local edits with global scans to catch these sorts of things, as well as making sure we aren't explaining things twice, etc.  (2) You tend to mix background with nods to our results, which is actually good to do, but it can be jarring if you go back and forth too much.  See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}\jessiet{Noted boss man}

@@

%The proof takes its inspiration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
%This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
%As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}. \jessiet{How to rephrase this?}
\botodo{I suggest cutting this paragraph entirely if we keep the full proof in. We mention above that it takes inspiration from Ramaswamy.}\jessiet{agreed; cutting this paragraph}

@@

\begin{proposition}
	When $\R$ is finite, a continuous loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
\end{proposition}\jessiet{Okay if $\Gamma$ is empty}
\begin{proof}
$\implies$
	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u \exploss{L}{u}{p}$.
	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $\exploss{L}{u_m}{p} \to \risk{L}(p)$.  
	Now we have $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Definition~\ref{def:calibrated-general}.
%	
% Commented out 05.19.2020 for easier proof if Lemma 5 is true.
%	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
%	
%	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
%	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
%	
%	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
%	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.

@@

Moreover, we have calibration implying indirect elicitation.
\begin{lemma}\label{lem:calib-implies-indir}
	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
  \raft{Use $\Gamma(p) \neq \emptyset$ here!}
	As $p \in \Gamma_u$, then $\zeta(\exploss{L}{u}{p} - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
\end{proof}

@@

Since $\gamma$ is not elicitable, we cannot apply Theorem~\ref{thm:cvx-flats} for the distribution $p = (1/8, 3/4,1/8)$\jessiet{Intuitively, because FSD would be lowest at that distribution, .... This is the one that FSD would give you a tightest dimension}, since $\gamma(p) = \{$rainy, snowy, sunny$\}$.
\citet[Theorem 16]{ramaswamy2016convex} cannot draw any conclusions about this property for two reasons that go hand in hand: first, we are given a target property instead of a target loss.
Second, since the property is not elicitable (hence why there can be no target loss), we observe $\dim(\Sc_{\gamma_{\text{rainy}}}(p)) \neq \dim(\Sc_{\gamma_{\text{sunny}}}(p))$, so their result cannot be applied as~\citet[Lemma 23]{ramaswamy2016convex} does not hold.

However, our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $q$ while staying in just one level set on the simplex.

>>>>

\begin{abstract}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous work implicitly relied on calibration essentially \raf{Tried ``essentially''} only via property elicitation. 
For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

@@

Motivated by structural prediction and other problems with exponentially or infinitely large label sets, we are particularly interested in the \emph{prediction dimension} of a surrogate: the dimension $d$ of its prediction space $\reals^d$.
A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension typically increases the computational\botodo{and sample?}\raft{I think so, but not sure -- you'd probably know better} complexity of learning.
We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
%\raft{FYI Jessie: what used to be this last paragraph still didn't quite get where you want to be in terms of motivating the problem.  I'd suggest taking a careful look at the diff at some point to see what I changed and ask me if you don't see why.  Probably the biggest issue was in laying out the gap.  You often need to give more detail about what \emph{has} been done to say what hasn't.}

@@

Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
%\raft{Nice!  Love ``proxies'' here.}
In the case of a discrete target loss, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and high-confidence classification~\citep{ramaswamy2018consistent}.
%\raft{FYI Jessie: Two general points.  (1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.  Next time it would be more efficient if you made sure to balance local edits with global scans to catch these sorts of things, as well as making sure we aren't explaining things twice, etc.  (2) You tend to mix background with nods to our results, which is actually good to do, but it can be jarring if you go back and forth too much.  See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}\jessiet{Noted boss man}

@@

%The proof takes its inspiration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
%This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
%As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}. \jessiet{How to rephrase this?}
%\botodo{I suggest cutting this paragraph entirely if we keep the full proof in. We mention above that it takes inspiration from Ramaswamy.}\jessiet{agreed; cutting this paragraph}

@@

\begin{proposition}
	When $\R$ is finite, a continuous loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
\end{proposition}\btw{Okay if $\Gamma$ is empty}
\begin{proof}
$\implies$
	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u \exploss{L}{u}{p}$.
	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $\exploss{L}{u_m}{p} \to \risk{L}(p)$.  
	Now we have $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Definition~\ref{def:calibrated-general}.
%	
% Commented out 05.19.2020 for easier proof if Lemma 5 is true.
%	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
%	
%	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
%	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
%	
%	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
%	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.

@@

Moreover, we have calibration implying indirect elicitation.
\begin{lemma}\label{lem:calib-implies-indir}
	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
	We know such a $u$ exists since $\Gamma(p) \neq \emptyset$.
	As $p \in \Gamma_u$, then $\zeta(\exploss{L}{u}{p} - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
\end{proof}

@@

Intuitively, since the feasible subspace dimension bound would be lowest at the distribution $p = (1/8, 3/4,1/8)$, we might want to test our Theorem~\ref{thm:cvx-flats} at $p$.
However, we cannot apply Theorem~\ref{thm:cvx-flats} at $p$ since $\gamma(p) = \{$rainy, snowy, sunny$\}$.
\citet[Theorem 16]{ramaswamy2016convex} cannot draw any conclusions about this property for two reasons that go hand in hand: first, we are given a target property instead of a target loss.
Second, since the property is not elicitable (hence why there can be no target loss), we observe $\dim(\Sc_{\gamma_{\text{rainy}}}(p)) \neq \dim(\Sc_{\gamma_{\text{sunny}}}(p))$, so their result cannot be applied as~\citet[Lemma 23]{ramaswamy2016convex} does not hold.

However, our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $q = (1/8, 3/4 - \epsilon, 1/8 + \epsilon)$ for a small enough $\epsilon > 0$, which we can apply since $\gamma(q) = \{$snowy$\}$, suggest that the convex elicitation complexity $\eliccvx(\gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $q$ while staying in just one level set on the simplex.
